---
title: "nearest_neighbors"
author: "Benjamin S. Wynia"
date: "September 30, 2017"
output: html_document
---
# Load Data
```{r}
properties <- read.csv("properties_2016.csv")

```

# Remove faulty tax assess values (less than $1000)
```{r}
properties$taxvaluedollarcnt[1:10]
properties$taxvaluedollarcnt[properties$taxvaluedollarcnt < 1000] <- NA
properties$taxvaluedollarcnt[1:10]

```

# Build Nearest Neighbors Dataset
```{r}
# New dataset with just the parcelid, longitude, and latitude
nn_dataset <- data.frame(properties$parcelid, properties$longitude, properties$latitude)
colnames(nn_dataset) <- c("parcelid","x","y")
# filter to only include complete cases (should be very few missing one of those variables)
nn_dataset <- nn_dataset[complete.cases(nn_dataset), ]
nrow(nn_dataset)
```

# Calculate Nearest Neighbors (10 point trial run)
```{r}
# this uses nn2 and a kd-tree to find nearest neighbors
neighbors_test <- nn2(data=nn_dataset[1:10,2:3], k=4, treetype ="kd")[[1]]
colnames(neighbors_test) <- c("Point","Neighbor 1","Neighbor 2","Neighbor 3")

```

# Test plot the trial run of Nearest Neighbors to Confirm 

```{r}
point_names <- as.vector(neighbors_test[1:10,1])

# Plot the first 10 points
plot <- ggplot(nn_dataset[1:10,], aes(nn_dataset[1:10,2],nn_dataset[1:10,3])) + geom_point() + geom_text(aes(label=point_names), hjust = 1, vjust = 1)
plot

# you can individually go through each of the 20 points and check that the algorithm identifies the 3 nearest neighbors
# I've selected three representative samples below
neighbors_test[1,]
neighbors_test[5,]
neighbors_test[10,]

```

# Test a trial run of the rows to parcelid swapping code
```{r}
# create empty vectors to store each parcel id
point_test <- as.vector(rep(0,nrow(nn_dataset[1:10,])))
neighbor_1_test  <- as.vector(rep(0,nrow(nn_dataset[1:10,])))
neighbor_2_test  <- as.vector(rep(0,nrow(nn_dataset[1:10,])))
neighbor_3_test  <- as.vector(rep(0,nrow(nn_dataset[1:10,])))

# iterate across the dataset, swapping parcelid for row number from the "neighbors" dataset
for (i in 1:nrow(neighbors_test)) {
  point_test[i] <- nn_dataset[i,1]
  neighbor_1_test[i] <- nn_dataset$parcelid[neighbors_test[i,2]]
  neighbor_2_test[i] <- nn_dataset$parcelid[neighbors_test[i,3]]
  neighbor_3_test[i] <- nn_dataset$parcelid[neighbors_test[i,4]]
}
neighborhood_test <- data.frame(point_test,neighbor_1_test, neighbor_2_test, neighbor_3_test)
colnames(neighborhood_test) <- c("parcelid","Neighbor 1","Neighbor 2","Neighbor 3")
neighborhood_test
```

# Plot the resulting test frame to ensure that neighbors are being correctly tagged with parcel_IDs

```{r}
point_names2 <- as.vector(neighborhood_test[1:10,1])
plot2 <- ggplot(nn_dataset[1:10,], aes(nn_dataset[1:10,2],nn_dataset[1:10,3])) + geom_point() + geom_text(aes(label=point_names2), hjust = 1, vjust = 2)
plot2
neighborhood_test[4,]
neighborhood_test[7,]
```

# Run the Nearest Neighbors algorithm on the entire dataset
The output of this is a dataframe with four columns. Column 1 is the first row of the nn_dataset, column 2, 3, and 4 are the "row numbers" of the nearest neighbors.
```{r}
neighbors <- nn2(data=nn_dataset[,2:3], k=4, treetype ="kd")[[1]]
colnames(neighbors) <- c("Point","Neighbor 1","Neighbor 2","Neighbor 3")
nrow(neighbors)
```

# Swap the row numbers for parcel_ids (Primary key for dataset)
We have to take the row numbers of the nearest neighbor, and plug that back into the original dataset to get the parcelid. This takes a couple minutes to run, and there is probably a better method than a "for" loop.

```{r}

# create empty vectors to store each parcel id
point <- as.vector(rep(0,nrow(nn_dataset)))
neighbor_1 <- as.vector(rep(0,nrow(nn_dataset)))
neighbor_2 <- as.vector(rep(0,nrow(nn_dataset)))
neighbor_3 <- as.vector(rep(0,nrow(nn_dataset)))

# iterate across the dataset, swapping parcelid for row number from the "neighbors" dataset
for (i in 1:nrow(neighbors)) {
  point[i] <- nn_dataset[i,1]
  neighbor_1[i] <- nn_dataset$parcelid[neighbors[i,2]]
  neighbor_2[i] <- nn_dataset$parcelid[neighbors[i,3]]
  neighbor_3[i] <- nn_dataset$parcelid[neighbors[i,4]]
}
neighborhood <- data.frame(point,neighbor_1, neighbor_2, neighbor_3)
colnames(neighborhood) <- c("parcelid","Neighbor 1","Neighbor 2","Neighbor 3")

```

Neighborhood is the dataset which has each parcelid in column 1 with the parcelid's of the three closest neighbors in columns 1, 2, and 3. We can use it for any queries where we want to test location as a determining factor.

# Use nearest-neighbors models

```{r}
# Simple model based on average tax value of 3 nearest neighbors

# Create a data.frame with only the variables used in the multivariable model previously
df.neighbor.variables <- data.frame(properties$parcelid, properties$taxvaluedollarcnt, properties$finishedsquarefeet12, properties$bathroomcnt, properties$garagecarcnt, properties$roomcnt, properties$yearbuilt, properties$regionidcity)
colnames(df.neighbor.variables) <- c("parcelid","actual.tax.value","actual.sqft","bathrooms","garages","room.count","year.built","regionidcity")

# Create a data.frame with only the parcel, tax value, and the finished square feet
df.taxvalue <- data.frame(properties$parcelid, properties$taxvaluedollarcnt, properties$finishedsquarefeet12)

# Eliminate cases with missing values
df.taxvalue <- df.taxvalue[complete.cases(df.taxvalue), ]
colnames(df.taxvalue) <- c("Neighbor","taxvalue","sqft")

# Calculate the tax assessed value per square foot for all properties in dataset
df.taxvalue$sqft.value <- df.taxvalue$taxvalue/df.taxvalue$sqft
colnames(df.taxvalue) <- c("parcelid","actual.tax.value","actual.sqft","actual.sqft.value")
# tax dataframe now includes parcel id, the actual tax value, the actual square feet, and the actual value per square foot
colnames(df.taxvalue) <- c("parcelid","actual.tax.value","actual.sqft","actual.sqft.value")


# Create a small subset of the neighbors for testing a nearest neighbors model
hood1 <- neighborhood

# Merge the tax characteristics (tax value, sqft, and value per square foot) with the neighbors dataset
# Merged 3 times, one for each neighbor
# Dataframe now has the parcel, the 3 neighbors parcel id's, and the tax value, sqft, and value per sqft for each neighbor
hood1 <- merge(hood1,df.taxvalue,by="parcelid")
colnames(df.taxvalue) <- c("Neighbor 1","taxvalue.nb1","sqft.nb1","sqft.value.nb1")
hood1 <- merge(hood1,df.taxvalue,by="Neighbor 1")
colnames(df.taxvalue) <- c("Neighbor 2","taxvalue.nb2","sqft.nb2","sqft.value.nb2")
hood1 <- merge(hood1,df.taxvalue,by="Neighbor 2")
colnames(df.taxvalue) <- c("Neighbor 3","taxvalue.nb3","sqft.nb3","sqft.value.nb3")
hood1 <- merge(hood1,df.taxvalue,by="Neighbor 3")

# Use the average value per square foot for the 3 neighbors to caclulate the sqft.value of the parcel
hood1$parcel.est.sqft.value <- (hood1$sqft.value.nb1 + hood1$sqft.value.nb2 + hood1$sqft.value.nb3)/3

# Multiply the value per square foot by the square footage of the tarfet parcel
hood1$parcel.est.value <- hood1$parcel.est.sqft.value*hood1$actual.sqft

# Filter out any cases with missing data
hood1 <- hood1[complete.cases(hood1),]

# Consolidate the important variables in a new data.frame
hood.consolidated <- data.frame(hood1$parcelid, hood1$parcel.est.sqft.value, hood1$parcel.est.value)
colnames(hood.consolidated) <- c("parcelid","parcel.est.sqft.value","parcel.est.value")

# Merge the estimated value with the original property variables (bathrooms, garage, etc.)
hood.consolidated <- merge(hood.consolidated,df.neighbor.variables, by = "parcelid" )
colnames(hood.consolidated) <- c("parcelid","parcel.est.sqft.value","parcel.est.value","actual.tax.value","actual.sqft","bathrooms","garages","room.count","year.built","regionidcity")

# Print top 10 rows for familiarization
#hood.consolidated[1:10,]

```

# Create a multivariable model using the estimated value per quare foot and other data

```{r}
# Check to make sure the data is relatively complete
length(which(is.na(hood.consolidated$bathrooms)))
length(which(is.na(hood.consolidated$garages)))
length(which(is.na(hood.consolidated$parcel.est.value)))

```

## Backwards variable selection method of model building
```{r}
hood_model <- lm(actual.tax.value ~ parcel.est.value + bathrooms + garages + room.count + year.built + regionidcity,na.action=na.exclude, data = hood.consolidated)
backwise_regression <- stepAIC(hood_model, direction="backward")
hood_r2 <- summary(backwise_regression)$adj.r.squared
hood_r2

```

## Multivariable Model
```{r}
# 
multivariable_model <- lm(taxvaluedollarcnt ~ finishedsquarefeet12 + bathroomcnt + garagecarcnt + roomcnt + yearbuilt + regionidcity,na.action=na.exclude, data = properties)
multi_r2 <- summary(multivariable_model)$adj.r.squared
#summary(multivariable_model)
multi_r2

# not sure why the R^2 dropped, maybe just because now I'm using full dataset, but R^2 came to 45.7%. 
```


```{r}

```

```{r}

```
